Reionization Planck 2018 Notes

### 2020-08-06 results/notes.tex
Updates from Overleaf

results/cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_1600.png

results/cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_800.png

results/cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_100.png

results/cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_50.png

>>>>

\begin{figure}
\includegraphics[width=0.4\textwidth]{cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_1600.png}
\includegraphics[width=0.4\textwidth]{cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_800.png}
\includegraphics[width=0.4\textwidth]{cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_100.png}
\includegraphics[width=0.4\textwidth]{cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_50.png}
\label{fig:}
\caption{Changing num\_bins = 1600 for the Fortran/cosmomc KDE w/ f = 0.14, which recovers close to the python KDE line w/ the same f. Lowering num\_bins increases smoothing.
} 
\end{figure}
